---
title: "Course 5, Week 2, Quiz 1"
author: "Michel Mariën"
date: "23 juli 2018"
output: html_document
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=12,warning=FALSE)
```

## Session Setup

```{r session setup, results="hide",message=FALSE}

library(dplyr)
library(ggplot2)
library(lubridate)
library(reshape2)
library(mice)
library(randomForest)

options(scipen=999)

```

## Upload data

```{r Upload data}

  bronmap<-"C:\\_Data\\Mijn Documenten\\R\\Scripts Coursera\\Course 5 - Week 2"
  
  data_raw_link<-paste(bronmap,"activity.csv",sep="\\")
  
  data_raw<-read.csv(data_raw_link,sep = ",",header = T,stringsAsFactors = F)

```

## Data cleaning

```{r Data cleaning}

  data_raw$rowno<-1:nrow(data_raw)

  data_raw$date<-ymd(data_raw$date)
  
  data_raw$weekday<-wday(data_raw$date)
  
  data_raw$dagnaam<-ifelse(data_raw$weekday>5,"Weekend","Week")
  
```

## Assignments

###  Assignment 1

###### Code for reading in the dataset and/or processing the data

See chunk {r Upload data}

###  Assignment 2

###### Histogram of the total number of steps taken each day

```{r Assignment 2}
Sum<-data_raw %>% group_by(date) %>% summarize(day_sum=sum(steps))

ggplot(Sum,aes(date,day_sum))+geom_col(col="black",fill="blue")+ylab("total no of steps/day")

```

###  Assignment 3

##### Mean and median number of steps taken each day


```{r Assignment 3}

Mean<-data_raw %>% group_by(date) %>% summarize(Mean = mean(steps, na.rm=TRUE))

head(Mean)

Median<-data_raw %>% group_by(date) %>% filter(steps>0) %>% 
    summarize(Median = median(steps, na.rm=TRUE))

head(Median)

dataset<-left_join(Mean,Median,by="date")

head(dataset)

```

###  Assignment 4

##### Time series plot of the average number of steps taken

```{r Assignment 4}

ggplot(dataset,aes(date,Mean))+geom_line(col="blue")+ylab("Mean (steps/day)")

```

###  Assignment 5

##### The 5-minute interval that, on average, contains the maximum number of steps


```{r Assignment 5}

Max <- data_raw %>% group_by(date)%>% filter(steps==max(steps))


head(Max)
```

###  Assignment 6

##### Code to describe and show a strategy for imputing missing data


```{r Assignment 6, cache=TRUE, results="hide"}

data_mice<-mice(data_raw, method="rf")
  
dataset_imp <- complete(data_mice)

```

###  Assignment 7

##### Histogram of the total number of steps taken each day after missing values are imputed

```{r Assignment 7}

Mean_imp<-dataset_imp %>% group_by(date) %>% summarize(mean=mean(steps))

ggplot(Mean_imp,aes(date,mean))+geom_col(col="black",fill="blue")

```


### Assignment 8

##### Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends

```{r Assignment 8}

Mean_imp$weekday<-wday(Mean_imp$date)

Mean_imp$dagnaam<-ifelse(Mean_imp$weekday>5,"Weekend","Week")

Mean_week<-dataset_imp  %>% group_by(dagnaam,interval) %>% summarize(Mean = mean(steps, na.rm=TRUE))

ggplot(Mean_week,aes(interval,Mean))+geom_line(aes(col=dagnaam))+facet_grid(.~dagnaam)+
  ggtitle("Number of steps per interval")

```


